Neuroecon Poster Figures

### 2017-10-04 code/NeuroeconPoster.Rmd
added new version based on feedback

p1 = fig_data_poster %>%
  filter(task == 'task') %>%
ggplot(aes(y = var, x = retest_reliability)) + 
  geom_point(aes(size=sample_size, shape = type), color='#00BFC4')+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
  theme(panel.spacing = unit(0.75, "lines"), 
        strip.placement = "outside",
        strip.text.y = element_text(angle=180, size=20),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey80"),
        legend.position = 'bottom') + 
  xlab("")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_shape_manual(breaks = sort(fig_data$type), values = c(15, 16, 17, 3))+
  geom_vline(xintercept = 0, color = "red", size = 1)

p2 = fig_data_poster %>%
  filter(task == 'survey') %>%
ggplot(aes(y = var, x = retest_reliability)) + 
  geom_point(aes(size=sample_size, shape = type), color = '#F8766D')+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
  theme(panel.spacing = unit(0.75, "lines"), 
        strip.placement = "outside",
        strip.text.y = element_text(angle=180, size=20),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey80")) + 
  xlab("")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_shape_manual(breaks = sort(fig_data$type), values = c(15, 17, 3))+
  geom_vline(xintercept = 0, color = "red", size = 1)

@@

```{r}
p9 = rel_df %>%
  ggplot(aes(icc, spearman, color=task))+
  geom_point()+
  geom_abline(intercept = 0, slope=1))+
  theme_bw()+
  theme(legend.position="bottom",
        legend.title = element_blank(),
        legend.text= element_text(size=30),
        axis.text.x = element_text(size=20),
        axis.text.y = element_text(size=20),
        axis.title.x = element_text(size = 30),
        axis.title.y = element_text(size = 30),
        strip.text = element_text(size=30))

>>>>

p1 = fig_data_poster %>%
  filter(task == 'task') %>%
ggplot(aes(y = var, x = retest_reliability)) + 
  geom_point(aes(size=sample_size, shape = type), color='#00BFC4')+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
  theme(panel.spacing = unit(0.75, "lines"), 
        strip.placement = "outside",
        strip.text.y = element_text(angle=180, size=36),
        axis.text.y = element_text(size=20),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey80"),
        legend.position = 'bottom') + 
  xlab("")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_shape_manual(breaks = sort(fig_data$type), values = c(15, 16, 17, 3))+
  geom_vline(xintercept = 0, color = "red", size = 1)

p2 = fig_data_poster %>%
  filter(task == 'survey') %>%
ggplot(aes(y = var, x = retest_reliability)) + 
  geom_point(aes(size=sample_size, shape = type), color = '#F8766D')+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
  theme(panel.spacing = unit(0.75, "lines"), 
        strip.placement = "outside",
        strip.text.y = element_text(angle=180, size=36),
        axis.text.y = element_text(size=20),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey80")) + 
  xlab("")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_shape_manual(breaks = sort(fig_data$type), values = c(15, 17, 3))+
  geom_vline(xintercept = 0, color = "red", size = 1)

@@

```{r}
p9 = rel_df %>%
  ggplot(aes(icc, spearman, color=task))+
  geom_point()+
  geom_abline(intercept = 0, slope=1)+
  theme_bw()+
  theme(legend.position="bottom",
        legend.title = element_blank(),
        legend.text= element_text(size=30),
        axis.text.x = element_text(size=20),
        axis.text.y = element_text(size=20),
        axis.title.x = element_text(size = 30),
        axis.title.y = element_text(size = 30),
        strip.text = element_text(size=30))
